Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-12 syntaxsemantics.tex
+

we see a physical memory $\mathsf{load}$ (i.e. physical memory map ($\sigma.\mathcal{M}$) for each level) for each level of page-table-walk concluded with alignment of the returned address for each \textit{successful} page-table-walk traversal what our reasoning principles only consider.

>>>>

we see a physical memory $\mathsf{load}$ (i.e. physical memory map ($\sigma.\mathcal{M}$) for each level) for each level of page-table-walk concluded with alignment of the returned address for each \textit{successful} page-table-walk traversal which is what our reasoning principles only consider.
